\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-03-25 cover_letter.tex
Fix typo.

Since the publication of ``Mapping the Antigenic and Genetic Evolution of Influenza Virus'' by Smith et al. in 2004, there has been significant interest in assessing patterns of antigenic and genetic evolution in seasonal influenza.
Such cartographic approaches use multidimensional scaling (MDS) to position viruses and antisera on an antigenic map so that distances between viruses and antisera predict observed serological data.
Here, we present a substantial advance to previous approaches that uses Bayesian multidimensional scaling (BMDS) to place antigenic cartography in a fully probabilistic framework.
Doing so has allowed us to build in important covariates into the statistical model; most importantly, phylogenetic relationships.
Thus, our method simultaneously models evolutionary and antigenic dynamics, and allows us to infer which phylogeny branches have evolved in antigenic phenotype and which branches have remained static.

>>>>

Since the publication of ``Mapping the Antigenic and Genetic Evolution of Influenza Virus'' by Smith et al.\ in 2004, there has been significant interest in assessing patterns of antigenic and genetic evolution in seasonal influenza.
Such cartographic approaches use multidimensional scaling (MDS) to position viruses and antisera on an antigenic map so that distances between viruses and antisera predict observed serological data.
Here, we present a substantial advance to previous approaches that uses Bayesian multidimensional scaling (BMDS) to place antigenic cartography in a fully probabilistic framework.
Doing so has allowed us to build in important covariates into the statistical model; most importantly, phylogenetic relationships.
Thus, our method simultaneously models evolutionary and antigenic dynamics, and allows us to infer which phylogeny branches have evolved in antigenic phenotype and which branches have remained static.
